Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-04-09 icmssp-paper/parts/02_03_facialrecognition.tex

Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem. Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
\begin{align}
    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
\end{align}

Computing for the distances within Paillier would just be multiplying the encrypted sums together.
\begin{equation}
	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
\end{equation}
The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ requires the use of the secure squaring protocol outlined in Table \ref{tab:flop_summary}.
% The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.

>>>>

Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem. Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}. Computation of the distances  uses the secure squaring protocol outlined in Table \ref{tab:flop_summary}.
% \begin{align}
%     d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
%         &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
% \end{align}

% Computing for the distances within Paillier would just be multiplying the encrypted sums together.
% \begin{equation}
% 	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
% \end{equation}
% The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ requires the use of the secure squaring protocol outlined in Table \ref{tab:flop_summary}.
% The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
